### 2014-04-16 doc/uist14/iteration3.tex
clarifying technique

\subsection{Technique}
The motion sensors (including gyroscope, magnetometer and accelerometer) on the
head-worn device can help us determine the orientation of a user's head.
Unfortunately, this absolute orientation cannot be directly used in any indoor
environment as the user may change their location. As long as the targets are
spread around the periphery, however, their relative orientations are stable
(see Figure~\ref{fig:third_principle}). This key observation inspires us to
investigate a hybrid solution with IR and orientation sensors on Glass.

>>>>

\subsection{Technique}
Using the motion sensors (including gyroscope, magnetometer and accelerometer) on the
head-worn device and IR, we can discover the spatial relationships between targets and the head orientation of the user.

Unfortunately, this absolute orientation cannot be applied to all indoor
environments, since the user’s movements through the space could change the relationships between targets. However, with the constraint that the targets are spread around the periphery, their relative orientations are stable
(see Figure~\ref{fig:third_principle}). This key observation inspires us to
investigate a hybrid solution using a combination of IR and orientation sensors on Glass.
